Using reference models in feature selection \vspace{.1in}

### 2019-12-04 paper/ref_approach.tex
move a paragraph to a later section

Here we repeat the selection of Section \ref{intro-example} via
stepwise backward regression. In this case, the overall number of
covariates (original plus noisy) is 100, as it was in the last part of
Section \ref{intro-example}. We compare results with and without using
a reference model on top of the procedure following our simple
reference model approach outlined in \eqref{eq:ref_mod}. Figure
\ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant
features included in the final model and the out-of-sample root mean
square error (RMSE). Results are based on 100 bootstrap samples on the
whole dataset, and the predictive performance is tested on the
observations excluded at each bootstrap sample. We observe that the
reference model reduces the number of irrelevant features included in
the final model. This leads to less overfitting and thus to improved
out-of-sample predictive performance in terms of RMSE. The reference
model approach applied to the stepwise backward regression achieves
outstanding improvements considering its simplicity, yet it does not
reach the goodness of the much more sophisticated projective
prediction approach (see results of Section \ref{intro-example}).
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
  \caption{Stepwise backward selection with and without using a reference model. The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
  \label{fig:bodyfat_step_refvsdata}
\end{figure}

@@

We conclude our complete selection experiments using the body fat dataset one
more time, which was already described in Section \ref{intro-example}. We
carry out two different analyses: one using the normal means problem
framework and another one using selection via stepwise backward
regression. In the former, we add noisy uncorrelated covariates to the
original data up to a total of 1000 features. These covariates are
normally distributed and scaled as the original covariates. We compute
correlations between each variable and the target variable, that is
the amount of fat, and transform them by Fisher-Z-transformation. The
original assumption in order for \eqref{eq:fisher_transformation} to
hold is that the variables are jointly normally distributed. In our
experience the normal approximation in
\eqref{eq:fisher_transformation} is still reasonable, but after
rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and
instead estimate it from the data. The methods we compare are those
used in Section \ref{complete-selection}: the control of the local
false discovery rate (loc.fdr), the empirical Bayes median (EB.med)
and the selection by posterior credible intervals at level 90\%
(ci.90).  In order to vary the difficulty of the selection, we
bootstrap subsamples of different sizes, going from $n=50$ up to
$n=251$ (i.e., the full size of the data). For each condition, results
are averaged over 100 bootstrap samples of the respective size.

>>>>

Here we repeat the selection of Section \ref{intro-example} via
stepwise backward regression. In this case, the overall number of
covariates (original plus noisy) is 100, as it was in the last part of
Section \ref{intro-example}. We compare results with and without using
a reference model on top of the procedure following a simple
reference model approach outlined in Equation \eqref{eq:ref_mod} 
of Section \ref{simulations}. Figure
\ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant
features included in the final model and the out-of-sample root mean
square error (RMSE). Results are based on 100 bootstrap samples on the
whole dataset, and the predictive performance is tested on the
observations excluded at each bootstrap sample. We observe that the
reference model reduces the number of irrelevant features included in
the final model. This leads to less overfitting and thus to improved
out-of-sample predictive performance in terms of RMSE. The reference
model approach applied to the stepwise backward regression achieves
outstanding improvements considering its simplicity, yet it does not
reach the goodness of the much more sophisticated projective
prediction approach (see results of Section \ref{intro-example}).
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
  \caption{Stepwise backward selection with and without using a reference model. The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
  \label{fig:bodyfat_step_refvsdata}
\end{figure}

@@

We conclude our complete selection experiments using the body fat dataset one
more time, which was initially described in Section \ref{intro-example}. We
carry out two different analyses: one using the normal means problem
framework and another one using selection via stepwise backward
regression. In the former, we add noisy uncorrelated covariates to the
original data up to a total of 1000 features. These covariates are
normally distributed and scaled as the original covariates. We compute
correlations between each variable and the target variable, that is
the amount of fat, and transform them by Fisher-Z-transformation. The
original assumption in order for \eqref{eq:fisher_transformation} to
hold is that the variables are jointly normally distributed. In our
experience the normal approximation in
\eqref{eq:fisher_transformation} is still reasonable, but after
rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and
instead estimate it from the data. The methods we compare are those
used in Section \ref{complete-selection}: the control of the local
false discovery rate (loc.fdr), the empirical Bayes median (EB.med)
and the selection by posterior credible intervals at level 90\%
(ci.90).  In order to vary the difficulty of the selection, we
bootstrap subsamples of different sizes, going from $n=50$ up to
$n=251$ (i.e., the full size of the data). For each condition, results
are averaged over 100 bootstrap samples of the respective size.
